A Switching Planner for Combined Task and Observation Planning

### 2010-11-22 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
Tiny changes to what Richard posted.
 - Charles

Finally, we come to the issue of valuing sequential plans, and
therefore giving the criterion that the sequential planner seeks to
optimise. Where $p_i$ is the probability that the $i^{th}$ action
execution is not a transition to $s^\bot$, we value a trace according
to:

@@

\noindent In goal directed problems, where the only non-zero reward is
received at the first transition to a goal state,
Eq~\ref{eq:tracevalue} corresponds exactly to the criteria of the
infamous degenerate hindsight system
\system{FFR$_a$}~\cite{yoon:etal:2007}. Form the perspective of
gradient-based reinforcement learning systems, such as William's
REINFORCE and GPOMDP variants for planning~\cite{olivier:doug:2009},
under reasonable assumptions the optimal trace yields a maximal
gradient step from a uniform soft-max policy.

>>>>

Finally, we come to valuing sequential plans, and therefore giving a
criterion that the sequential planner seeks to optimise. Where $p_i$
is the probability that the $i^{th}$ action execution is not a
transition to $s^\bot$, we value a trace according to:

@@

\noindent In other words, the value of a trace captures its
significance, in relation to other possible realisations of the plan,
to the overall expected value of the plan in
Eq~\ref{eq:expectedvalue}. In goal directed problems, where the only
non-zero reward is received at the first transition to a goal state,
Eq~\ref{eq:tracevalue} corresponds exactly to the criteria of the
infamous degenerate hindsight system
\system{FFR$_a$}~\cite{yoon:etal:2007}. Form the perspective of
gradient-based reinforcement learning systems, such as William's
REINFORCE and GPOMDP variants for planning~\cite{olivier:doug:2009},
under reasonable assumptions the optimal trace identifies a maximal
gradient step from a uniformly random soft-max policy.

%% Finally, we come to the issue of valuing sequential plans, and
%% therefore giving the criterion that the sequential planner seeks to
%% optimise. Where $p_i$ is the probability that the $i^{th}$ action
%% execution is not a transition to $s^\bot$, we value a trace according
%% to:

%% \begin{equation}\label{eq:tracevalue}
%% V(s_0, a_0, s_1, a_1,.., s_N) =  \prod_{i=1..N} p_i \sum_{i=1..N-1} \reward(\state_i, \action_i)
%% \end{equation}

%% \noindent In goal directed problems, where the only non-zero reward is
%% received at the first transition to a goal state,
%% Eq~\ref{eq:tracevalue} corresponds exactly to the criteria of the
%% infamous degenerate hindsight system
%% \system{FFR$_a$}~\cite{yoon:etal:2007}. Form the perspective of
%% gradient-based reinforcement learning systems, such as William's
%% REINFORCE and GPOMDP variants for planning~\cite{olivier:doug:2009},
%% under reasonable assumptions the optimal trace yields a maximal
%% gradient step from a uniform soft-max policy.
